{\bf {\Large Parameter sensitivity and identifiability for a biogeochemical model of hypoxia in the northern {G}ulf of {M}exico}}

### 2016-11-29 ident_manu.Rnw
moved supp tabs/figs to main text

<<sensalltile, eval = T, echo = F, fig.height = 6, fig.width = 3.5, out.width = '0.7\\textwidth', fig.cap = 'Sensitivity values (L1, \\cref{l1}) for local analyses of all state variables. Parameters are grouped by category: optics, organic matter, phytoplankton, zooplankton, temperature, and zoplankton.  See \\cref{tab:dosens} for L1 values for \\ac{do} and \\cref{tab:nh4sens,tab:chlsens,tab:irrsens,tab:no3sens,tab:om1sens,tab:om2sens,tab:po4sens} for the other state variables.'>>=
data(sens_ests_cat_all)

tmp <- reshape2::melt(sens_ests_cat_all, id.var = c('Parameter', 'error', 'Category'))

@@

toplo <- mutate(tmp,
    L1 = factor(L1, levels = rev(stts_lev), labels = rev(stts_lab))
  ) %>% 
  rename(Sensitivity = error)

toplo1 <- mutate(toplo, Parameter = as.character(par_txt(Parameter, frm = 'exp')))

@@

ggplot(toplo1, aes(y = Parameter, x = L1, fill = Sensitivity)) + 
  geom_tile(colour = 'black') + 
  pbase +
  scale_y_discrete('Parameter', 
    expand = c(0, 0),
    breaks = toplo1$Parameter, 
    labels = parse(text = toplo1$Parameter)
    ) + 
  scale_x_discrete('State variable', expand = c(0, 0)) +
  scale_fill_distiller(palette = "Spectral", trans = 'log10',  na.value = 'grey95') +
  facet_grid(Category~., scales = 'free_y', space = 'free') + 
  guides(fill = guide_colourbar(barheight = 0.5, barwidth = 10))

@@

ggplot(toplo, aes(x = Selected, y = coll)) + 
  geom_line() + 
  geom_text_repel(aes(label = Parameter), size = 3,
    parse = TRUE,
    point.padding = unit(0, "lines"),
    box.padding = unit(1, "lines"), 
    force = 3
    ) +
  geom_point(aes(fill = Category), shape = 21, size = 4) +
  geom_hline(yintercept = 15, linetype = 'longdash', colour = 'darkgrey') + 
  geom_hline(yintercept = 10, linetype = 'dotted', colour = 'darkgrey') + 
  facet_wrap(~L1, scales= 'free', ncol = 4) + 
  scale_y_continuous('Identifiability') + 
  scale_x_continuous(
    'Parameters selected by sensitivity',
    breaks = toplo$Selected, 
    expand = c(.1, .1)
    ) + 
  cols +
  pthm +
  theme(legend.position = 'top')
@

@@

@
\clearpage

%%
% sup figs

% effects of changing initial and structural conditions
<<inistreval, fig.cap = 'Effects of initial and structural conditions on parameter sensitivity.', fig.height = 7, fig.width = 8, out.width = '\\textwidth', eval = T, echo = F, warning = F, message = F>>=
# initial conditions
data(ini_eval)
data(struct_eval)

>>>>

% effects of changing initial and structural conditions
<<sensalltile, fig.cap = 'Sensitivity values (L1, \\cref{l1}) of all state variables to changes in parameter values using default conditions, changes in initial conditions (April, September seasonal means, \\cref{tab:inits}), and changes in structural complexity (\\cref{tab:strcs}). Parameters are grouped by category: optics, organic matter, phytoplankton, zooplankton, temperature, and zoplankton.  See \\cref{tab:dosens} for L1 values for \\ac{do} and \\cref{tab:nh4sens,tab:chlsens,tab:irrsens,tab:no3sens,tab:om1sens,tab:om2sens,tab:po4sens} for the other state variables.', fig.height = 7, fig.width = 8, out.width = '\\textwidth', eval = T, echo = F, warning = F, message = F>>=
# initial conditions
data(ini_eval)
data(struct_eval)

@@

@@

@@

ggplot(toplo, aes(x = Selected, y = coll)) + 
  geom_line() + 
  geom_text_repel(aes(label = Parameter), size = 3,
    parse = TRUE,
    point.padding = unit(0, "lines"),
    box.padding = unit(1, "lines"), 
    force = 3
    ) +
  geom_point(aes(fill = Category), shape = 21, size = 4) +
  geom_hline(yintercept = 15, linetype = 'longdash', colour = 'darkgrey') + 
  geom_hline(yintercept = 10, linetype = 'dotted', colour = 'darkgrey') + 
  facet_wrap(~L1, scales= 'free', ncol = 4) + 
  scale_y_continuous('Identifiability') + 
  scale_x_continuous(
    'Parameters selected by sensitivity',
    breaks = toplo$Selected, 
    expand = c(.1, .1)
    ) + 
  cols +
  pthm +
  theme(legend.position = 'top')

@@

%%
% sup figs
% NULL

### 2016-11-29 ident_manu.tex
moved supp tabs/figs to main text

\definecolor{fgcolor}{rgb}{0.345, 0.345, 0.345}
\newcommand{\hlnum}[1]{\textcolor[rgb]{0.686,0.059,0.569}{#1}}%
\newcommand{\hlstr}[1]{\textcolor[rgb]{0.192,0.494,0.8}{#1}}%
\newcommand{\hlcom}[1]{\textcolor[rgb]{0.678,0.584,0.686}{\textit{#1}}}%
\newcommand{\hlopt}[1]{\textcolor[rgb]{0,0,0}{#1}}%
\newcommand{\hlstd}[1]{\textcolor[rgb]{0.345,0.345,0.345}{#1}}%
\newcommand{\hlkwa}[1]{\textcolor[rgb]{0.161,0.373,0.58}{\textbf{#1}}}%
\newcommand{\hlkwb}[1]{\textcolor[rgb]{0.69,0.353,0.396}{#1}}%
\newcommand{\hlkwc}[1]{\textcolor[rgb]{0.333,0.667,0.333}{#1}}%
\newcommand{\hlkwd}[1]{\textcolor[rgb]{0.737,0.353,0.396}{\textbf{#1}}}%
\let\hlipl\hlkwb

@@

\begin{singlespace}
\title{{\bf {\Large Parameter sensitivity and identifiability for a biogeochemical model of hypoxia in the northern {G}ulf of {M}exico}}}
\author{
  {\bf {\normalsize Marcus W. Beck$^1$, John C. Lehrter$^2$, Lisa L. Lowe$^3$}}
  \\\\{\textit {\normalsize $^1$USEPA National Health and Environmental Effects Research Laboratory}}
  \\{\textit {\normalsize Gulf Ecology Division, 1 Sabine Island Drive, Gulf Breeze, FL 32561}}
	\\{\textit {\normalsize Phone: 850-934-2480, Fax: 850-934-2401}}
	\\{\textit {\normalsize Email: \href{mailto:beck.marcus@epa.gov}{beck.marcus@epa.gov}}}
	  \\\\{\textit {\normalsize $^2$Dauphin Island Sea Lab, University of South Alabama}}
  \\{\textit {\normalsize Dauphin Island, AL 36528}}
	\\{\textit {\normalsize Phone: 251-861-2141 ext. 7567}}
	\\{\textit {\normalsize Email: \href{mailto:jlehrter@disl.org}{jlehrter@disl.org}}}
	\\\\{\textit {\normalsize $^3$Lockheed Martin IS \& GS - Civil, supporting the USEPA}}
	\\{\textit {\normalsize Resarch Triangle Park, NC 27709}}
	\\{\textit {\normalsize Phone: 919-541-3985,}}
	\\{\textit {\normalsize Email: \href{mailto:lowe.lisa@epa.gov}{lowe.lisa@epa.gov}}}
  \vspace{1in} 
  \\ Version Date:   Mon Nov 28 16:09:57 2016 -0600
	}
\date{}
\maketitle
\end{singlespace}
\clearpage

@@

\footnotesize *Temperaure parameters apply to phytoplankton ($p1$, one group) or zooplankton ($z1$, one group), denoted by subscripts\end{table}

@@

\begin{figure}[!ht]

{\centering \includegraphics[width=0.7\textwidth]{figs/sensalltile-1}

@@

\caption{Sensitivity values (L1, \cref{l1}) for local analyses of all state variables. Parameters are grouped by category: optics, organic matter, phytoplankton, zooplankton, temperature, and zoplankton.  See \cref{tab:dosens} for L1 values for \ac{do} and \cref{tab:nh4sens,tab:chlsens,tab:irrsens,tab:no3sens,tab:om1sens,tab:om2sens,tab:po4sens} for the other state variables.}\label{fig:sensalltile}
\end{figure}

@@

%%
% sup figs

{\centering \includegraphics[width=\textwidth]{figs/inistreval-1}

\caption[Effects of initial and structural conditions on parameter sensitivity]{Effects of initial and structural conditions on parameter sensitivity.}\label{fig:inistreval}
\end{figure}

>>>>

\definecolor{fgcolor}{rgb}{0.345, 0.345, 0.345}
\newcommand{\hlnum}[1]{\textcolor[rgb]{0.686,0.059,0.569}{#1}}%
\newcommand{\hlstr}[1]{\textcolor[rgb]{0.192,0.494,0.8}{#1}}%
\newcommand{\hlcom}[1]{\textcolor[rgb]{0.678,0.584,0.686}{\textit{#1}}}%
\newcommand{\hlopt}[1]{\textcolor[rgb]{0,0,0}{#1}}%
\newcommand{\hlstd}[1]{\textcolor[rgb]{0.345,0.345,0.345}{#1}}%
\newcommand{\hlkwa}[1]{\textcolor[rgb]{0.161,0.373,0.58}{\textbf{#1}}}%
\newcommand{\hlkwb}[1]{\textcolor[rgb]{0.69,0.353,0.396}{#1}}%
\newcommand{\hlkwc}[1]{\textcolor[rgb]{0.333,0.667,0.333}{#1}}%
\newcommand{\hlkwd}[1]{\textcolor[rgb]{0.737,0.353,0.396}{\textbf{#1}}}%

@@

\begin{singlespace}
\title{{\bf {\Large Parameter sensitivity and identifiability for a biogeochemical model of hypoxia in the northern {G}ulf of {M}exico}}}
\author{
  {\bf {\normalsize Marcus W. Beck$^1$, John C. Lehrter$^2$, Lisa L. Lowe$^3$}}
  \\\\{\textit {\normalsize $^1$USEPA National Health and Environmental Effects Research Laboratory}}
  \\{\textit {\normalsize Gulf Ecology Division, 1 Sabine Island Drive, Gulf Breeze, FL 32561}}
	\\{\textit {\normalsize Phone: 850-934-2480, Fax: 850-934-2401}}
	\\{\textit {\normalsize Email: \href{mailto:beck.marcus@epa.gov}{beck.marcus@epa.gov}}}
	  \\\\{\textit {\normalsize $^2$Dauphin Island Sea Lab, University of South Alabama}}
  \\{\textit {\normalsize Dauphin Island, AL 36528}}
	\\{\textit {\normalsize Phone: 251-861-2141 ext. 7567}}
	\\{\textit {\normalsize Email: \href{mailto:jlehrter@disl.org}{jlehrter@disl.org}}}
	\\\\{\textit {\normalsize $^3$Lockheed Martin IS \& GS - Civil, supporting the USEPA}}
	\\{\textit {\normalsize Resarch Triangle Park, NC 27709}}
	\\{\textit {\normalsize Phone: 919-541-3985,}}
	\\{\textit {\normalsize Email: \href{mailto:lowe.lisa@epa.gov}{lowe.lisa@epa.gov}}}
  \vspace{1in} 
  \\ Version Date:   Mon Nov 28 17:05:13 2016 -0600
	}
\date{}
\maketitle
\end{singlespace}
\clearpage

@@

\footnotesize *Temperature parameters apply separately to phytoplankton ($p1$, one group) or zooplankton ($z1$, one group), denoted by subscripts\end{table}

@@

{\centering \includegraphics[width=\textwidth]{figs/sensalltile-1}

@@

\caption{Sensitivity values (L1, \cref{l1}) of all state variables to changes in parameter values using default conditions, changes in initial conditions (April, September seasonal means, \cref{tab:inits}), and changes in structural complexity (\cref{tab:strcs}). Parameters are grouped by category: optics, organic matter, phytoplankton, zooplankton, temperature, and zoplankton.  See \cref{tab:dosens} for L1 values for \ac{do} and \cref{tab:nh4sens,tab:chlsens,tab:irrsens,tab:no3sens,tab:om1sens,tab:om2sens,tab:po4sens} for the other state variables.}\label{fig:sensalltile}
\end{figure}

@@

%%
% sup figs
% NULL
